\PassOptionsToPackage{sort&compress}{natbib}
\documentclass[preprint]{elsarticle}

% \usepackage{natbib} not needed. Already added by elsarticle
\setcitestyle{numbers,round}

% To remove square brackets from reference list
\makeatletter 
\renewcommand\@biblabel[1]{#1} 
\makeatother

\usepackage{lineno,hyperref}
\modulolinenumbers[1]

% For equations
\usepackage{amsmath}
\usepackage{amssymb}

% Highlight
\usepackage{soul,xcolor}

% For the table
\usepackage{booktabs}
\usepackage{geometry}
\usepackage{array}

% To add notes to margins
\usepackage[colorinlistoftodos]{todonotes}

% To force figure position
\usepackage{float}

% To striketrough
\usepackage[normalem]{ulem}

\journal{Aperture}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style
%and % remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered \bibliographystyle{model1-num-names}

%% Numbered without titles \bibliographystyle{model1a-num-names}

%% Harvard
% \bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}
\bibliographystyle{vancouver}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style \bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style \usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style \bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}

\title{Hemodynamic Deconvolution Demystified: Sparsity-Driven Regularization at Work}

%% Group authors per affiliation:
\author[bcbl,upv]{Eneko Uru\~nuela\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding authors}
\ead{e.urunuela@bcbl.eu}

\author[epfl,chuv]{Thomas A.W. Bolton}
\author[epfl,unige]{Dimitri Van De Ville}
\author[bcbl]{C\'{e}sar Caballero-Gaudes\corref{mycorrespondingauthor}}
\ead{c.caballero@bcbl.eu}

\address[bcbl]{Basque Center on Cognition, Brain and Language (BCBL),
Donostia-San Sebasti\'{a}n, Spain.} \address[upv]{University of the Basque
Country (EHU/UPV), Donostia-San Sebasti\'{a}n, Spain.}
\address[epfl]{Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Lausanne, Switzerland.}
\address[chuv]{Gamma Knife Center, Department of Clinical Neuroscience, Centre Hospitalier Universitaire Vaudois (CHUV), Lausanne, Switzerland}
\address[unige]{Faculty of Medicine, University of Geneva, Geneva, Switzerland}

\begin{abstract}
\input{sections/abstract.tex}
\end{abstract}

\begin{keyword}
fMRI deconvolution, paradigm free mapping, total activation, temporal
regularization
\end{keyword}

\end{frontmatter}

\linenumbers

% Introduction
\input{sections/introduction.tex}

% Theory
\input{sections/theory.tex}

% Methods
\input{sections/methods.tex}

% Results
\input{sections/results.tex}

% Discussion
\input{sections/discussion.tex}

\section{Code and data availability}
\label{sec:github}
The code and materials used in this work can be found in the following GitHub
repository: \url{https://github.com/eurunuela/pfm_vs_ta}. We encourage the
reader to explore the parameters (e.g., SNR, varying HRF options and mismatch
between algorithms, TR, number of events, onsets, and durations) in the provided
Jupyter notebooks. Likewise, the data used to produce the figures can be found
in \url{https://osf.io/f3ryg/}.

\section{Acknowledgements}
We thank Stefano Moia and Vicente Ferrer for data availability, and Younes
Farouj for valuable comments on the manuscript. This research was funded by the
Spanish Ministry of Economy and Competitiveness (RYC-2017-21845), the Basque
Government (BERC 2018-2021, PIB\_2019\_104, PRE\_2020\_2\_0227), and the Spanish
Ministry of Science, Innovation and Universities (PID2019-105520GB-100), and the
Swiss National Science Foundation (grant 205321\_163376).

\section{CRediT}
Eneko Uru\~nuela: Conceptualisation, Methodology, Software, Formal Analysis,
Investigation, Data Curation, Writing (OD), Writing (RE), Visualisation, Funding
acquisition. Thomas A.W. Bolton: Conceptualisation, Methodology, Writing (RE).
Dimitri Van de Ville: Conceptualisation, Methodology, Writing (RE). C\'{e}sar
Caballero-Gaudes: Conceptualisation, Methodology, Software, Formal Analysis,
Investigation, Data Curation, Writing (OD), Writing (RE), Visualisation, Funding
acquisition.

\bibliography{mybibfile}

\newpage
\input{sections/supplementary.tex}

\end{document}